\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{makecell}

\geometry{margin=1in}

\title{Computational Modelling of Somatosensory Laminar Circuits}
\author{Rosa Großmann}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Changed stuff
\end{abstract}

\section{Introduction}
Briefly introduce the biological background and motivation for the modelling project.

\section{Methods}
\subsection{Model Description}
\subsection{Model Parameters and Units}


\textbf{Connectivity Matrix}
PSPs (Synaptic Strengths) mV
W matrix : mV 
potential
rate Hz 
timestep sec
tau (membrane time constant) sec


SI Units:
V
Hz 
sec




\subsection{Connectivity Matrix}
The connectivity value that weights the connection between two population depends on three factors:
Connection probability: what is the probability that a neuron from population A connects to a neuron in population B. 
The probablity is computed by conducting pairwise bernoulli trials. Example: we look at layer 4 and pick one PV cell and check if it connects to 
each of the SOM cells. 
Multapses (multiple synapses between the same pair of neurons) are lumped together.
Synaptic strength: what is the post-synaptic potential (PSP) change induced by a single pre-synaptic spike. 
The synaptic strength also reflects increased potential due to multapses (since a stronger PSP would arise).
Cell count: how many neurons are in population A.
The thalamus cell counts are computed using the summarized cell count of one column (Area 1)
The paper by \cite{Jiang2023} provides synaptic strength values, which are given as post-synaptic potential changes in mV (see Table 3 on page 6 of the preprint).
 

The connectivity value is then calculated as:
\begin{equation}
\text{Connectivity Value} = \text{Synaptic Strength} \times \text{
Connection Probability} \times \text{Cell Count}
\end{equation}

Table \ref{tab:connectivity} summarizes the sources of the values used for each factor that build the connectivity matrix.
\begin{table}[h!]
\centering
\caption{Sources of values for the connectivity matrix.}
\begin{tabular}{lcccc}
\hline
 & Synaptic strength & Connection probablity & Cell count \\
\hline
Area 1 & Jiang et al. 2023 & Jiang et al. 2023 & Jiang et al. 2023 \\
Area 3b & collapsed Area 1 & collapsed Area 1 & Jiang et al. 2023 (collapsed) \\
S2 & same as Area 1 & same as Area 1 & adapted from Area 1 \\
Thalamus 4 & Jiang et al. 2023 & \makecell{Jiang et al. 2023 \\ partly assumed by \\the authors} & ? \\
\hline
\end{tabular}
\label{tab:connectivity}
\end{table}

\section{Results}
Present the main findings, including figures and tables.

\section{Discussion}
Interpret the results and discuss their implications.

\section{Conclusion}
Summarize the main outcomes and future directions.

\bibliographystyle{plain}
\bibliography{references}

\end{document}